Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-22 Paper/ms.tex
Numbers updated in Gliese 581 section

\begin{figure}
\includegraphics[scale=0.45]{Figures/logl0.eps}
\caption{Log likelihood vs. enclosed prior mass (a standard output of Nested
Sampling algorithms) for the $\nu$ Oph analysis.
There are several phase transitions (concave-up regions) present. The one at
$\log(X) \approx -75$ separates models which contain additional signals from
models that do not. Without using Nested Sampling it would be very difficult
to mix between these two situations and calculate the posterior probability
for the existence of the additional signals.
\label{fig:logl0}}
\end{figure}

Figure~\ref{fig:logl0} shows the relationship between the likelihood $L$
and the enclosed prior mass $X$ for the $\nu$ Oph analysis. These plots are
a standard output of Nested Sampling analyses, and provide
insights into the structure of the problem. Concave-up regions of this curve
indicate phase transitions which can cause severe problems for annealing-based
methods, and sometimes even for sampling the posterior distribution. In this
analysis, the models with a third signal exist to the left of the phase
transition at $\log(X) \approx -75$, and models without the signal exist to the
right of the phase transition. Mixing between these two phases is crucial for
accurately computing the posterior probability that extra signals exist.
However, if we had simply tried to sample the posterior distribution, it would
not mix easily between these two phases and could easily fail to detect the
extra signals.

@@

The posterior distribution for $N$ is shown in Figure~\ref{fig:gliese581_N},
and shows strong evidence for at least eight periods
($P(N \leq 7 | D) = 0.004$).
It is now recognised that
there are many possible sources for oscillations in a data set and not all
such oscillations should be claimed as planets \citep{2014Sci...345..440R}. 
Our model cannot distinguish between oscillations due to planets and
oscillations due to stellar activity: any oscillations found in the dataset
will be described as ``planets'' by the model. However it is interesting that
we find many more signals in the data than previous authors.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Fengji Hou and David Hogg (NYU) for inspiring me to
finally work on this problem, and Phil Gregory (UBC) for writing so many
interesting papers on it. We also thank Tom Loredo (Cornell) and Dan
Foreman-Mackey (NYU) for interesting conversations and feedback, and Ben
Montet (Caltech) and Geraint Lewis (Sydney) for helpful discussions.

>>>>

\begin{figure}
\includegraphics[scale=0.45]{Figures/logl0.eps}
\caption{Log likelihood vs. enclosed prior mass (a standard output of Nested
Sampling algorithms) for the $\nu$ Oph analysis.
There are several phase transitions (concave-up regions) present. The one at
$\log(X) \approx -70$ separates models which contain additional signals from
models that do not. Without using Nested Sampling it would be more difficult
to mix between these two situations and calculate the posterior probability
for the existence of the additional signals.
\label{fig:logl0}}
\end{figure}

Figure~\ref{fig:logl0} shows the relationship between the likelihood $L$
and the enclosed prior mass $X$ for the $\nu$ Oph analysis. These plots are
a standard output of Nested Sampling analyses, and provide
insights into the structure of the problem. Concave-up regions of this curve
indicate phase transitions which can cause severe problems for annealing-based
methods, and sometimes even for sampling the posterior distribution. In this
analysis, the models with a third signal exist to the left of the phase
transition at $\log(X) \approx -70$, and models without the signal exist to the
right of the phase transition. Mixing between these two phases is crucial for
accurately computing the posterior probability that extra signals exist.

@@

The posterior distribution for $N$ is shown in Figure~\ref{fig:gliese581_N},
and shows strong evidence for at least eight periods
($P(N \leq 7 | D) = 0.012$).
It is now recognised that
there are many possible sources for oscillations in a data set and not all
such oscillations should be claimed as planets \citep{2014Sci...345..440R}. 
Our model cannot distinguish between oscillations due to planets and
oscillations due to stellar activity: any oscillations found in the dataset
will be described as ``planets'' by the model. However it is interesting that
we find many more signals in the data than previous authors.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Fengji Hou and David Hogg (NYU) for inspiring me to
finally work on this problem, and Phil Gregory (UBC) for writing so many
interesting papers on it. We also thank Tom Loredo (Cornell) and Dan
Foreman-Mackey (NYU) for interesting conversations and feedback, and Ben
Montet (Caltech) and Geraint Lewis (Sydney) for helpful discussions.
The referee also provided excellent suggestions for improving the manuscript.
